---
title: "CDEC_QA_4"
author: "Catarina Pien"
date: "September 17, 2018"
output: html_document
description: QAQC Steps for CDEC data
editor_options: 
chunk_output_type: console
---

Start by clearing the environment.

```{r clean, include = FALSE}
rm(list=ls(all=TRUE))
```

## Load files, edit variable names

* Filter out those that are not contiguous/ not active
* Add datetime sorting variables
```{r setup}
library(tidyverse)
library(readr)
library(lubridate)
library(TTR) # rate of change
library(caTools) # rate of change

setwd("C:/Users/cpien/OneDrive - California Department of Water Resources/Work/ClimateChange/R_code/")
#### Read files ###
temp_H_0 <- readRDS("climatechange/WaterTemp/data/Temp_all_H.rds")

# Filter out stations that are not contiguous.
temp_H <- temp_H_0 %>% 
  filter(!station %in% c("CNT", "CPP", "DAR", "DMC", "DYR","ECD", "HBP", "KA0", "ROR", "DV7", "BOY"))

# Remove unnecessaries
rm(temp_H_0)
```

## QA1) Remove days with less than 20 values 

1. Count the number of rows per station, date group. (There should only be one row per date)
2. To be deleted: Filter out dates for which there are less than 20 values (out of 24).
3. Use antijoin to remove the deleted dates from original data frame.

```{r Missing Values, message = FALSE}

# This data frame contains all the dates with less than 20 values. 
temp_q1_a <- temp_H %>%
  group_by(station, date) %>%
  arrange(station, date, hour) %>%
  summarize(total = n()) %>%
  mutate(Flag_QC1 = ifelse(total < 20, "Y", "N"))

# Values that are flagged
temp_q1_b <- temp_q1_a %>%
  filter(Flag_QC1 == "Y")

#Join original dataframe with flagged values based on values NOT in common. 
#based on station and date
temp_q1 <- temp_H %>%
  left_join(temp_q1_a, by = c("station", "date"))

# Remove unnecessaries
rm(temp_q1_a)
gc()

```

## QA2) Remove if there are more than 12 repeating values in a row

1. Create new columns indicating whether the temperature at x hour is the same as that of x-1 hours, x-2 hours, x-3 hours, x-4 hours. (1 = yes, 0 = no)
2. Add the columns up. If all values are the same, "delete"  = 4. 
3. Filter out rows to be deleted. 
4. Use antijoin to extract dates that are not in the "delete" data frame. 
    + Note: the "delete" data frame has only the rows where delete = 4, but we want to delete the entire day if there are repeating values, so we need to specify by = station, date. 

```{r repeating values, message = FALSE}

# Function to determine whether values are repeating by each station
# Inputs are data frame and x (number of repeating values you want to check for)
repeating_values <- function(df, x) {
  df %>% 
    group_by(station) %>%
    arrange(station, date, hour)
  for (i in 1:x) {
    print(i)
    same <- paste0('same', i)
    df[[same]]<- ifelse(df$Temp == lag(df$Temp, n = i), 1, 0)
  }
  return(df)
    }

### --------------------------------------------------
temp_q1$Temp <- as.numeric(temp_q1$Temp)

# Run function repeating values. 
# Tally up "same" columns (same_total)
# Create column "delete" - if same_total = x (represented by max(same_total), delete = Y)
temp_q2_a <- repeating_values(df = temp_q1, x = 10) %>% 
  mutate(same_total = as.numeric(rowSums(select(., contains("same"))))) %>%
  mutate(Flag_QC2_a = ifelse(same_total == max(same_total, na.rm = TRUE),"Y", "N")) %>%
  dplyr::select(-starts_with("same"))

###---------------------------------------------------------
### Rosie: Attempt to apply flags to all repeating values:::
test = temp_q2_a

test$Flag_QC2_b = NA

for (i in 1:nrow(test)) {
ifelse(test$Flag_QC2_a[i] == "Y", 
      for (j in 1:18) test$Flag_QC2_a2[i-j] =="Y", "N")

}
###-------------------------------------------------------------

# Create another flag that applies the "Y" to the whole day
temp_q2 <- temp_q2_a %>%
  group_by(station, date)%>%
  mutate(Flag_QC2_b = ifelse("Y" %in% Flag_QC2_a, "Y", "N"))

# Create a dataframe of all the flagged rows
temp_q2_b <- temp_q2 %>%
  filter(Flag_QC2_b == "Y")

# Remove unnecessaries
rm(temp_q2_a, temp_q1)
gc()

# Look at how often there are less than 24 observations
obs <- temp_q2 %>%
  group_by(station, date)%>%
  summarize(obs = n()) %>%
  filter(obs<24)
```

### QA3: Rate of change and Spike test
```{r Rate of Change}
### ---------------------------------------------
# Q3: Temp - Temp-1
# sdev_th: Determined threshold for too high of a rate of change (3 * SD(Temp) over 25 days)
# If Q3 > sdev_th, flag.
# Additionally, if Q3 > 5 (5 degree change in 15 minutes), flag. 

temp_q3_a <- temp_q2 %>%
  group_by(station) %>%
  arrange(station, datetime) %>%
  mutate(QC3 = abs(Temp- lag(Temp, n = 1)))%>%
  mutate(sdev_th = 3 * runSD(Temp, 25))%>%
  mutate(Flag_QC3 = ifelse((QC3 > sdev_th | QC3 > 5), "Y", "N")) %>%
  ungroup()

temp_q3_b <- temp_q3_a %>%
  filter(Flag_QC3 == "Y")

temp_q3 <- temp_q3_a %>%
  select(-c(sdev_th, QC3))

rm(temp_q3_a)

```



## QA4): Remove anything outside of reasonable temperature range (0-40)
```{r 0-40, message = FALSE}
temp_q4 <- temp_q3%>%
mutate(Flag_QC4 = ifelse(Temp<0 | Temp>40, "Y", "N"))

############TEMPORARY ONLY##########

temp_q4d <- temp_q2%>%
  filter(Temp>0 & Temp<40)

```


## Calculating temperature differences 

```{r Temp differences}
Tdiffs_all <- temp_q4d %>%
  group_by(station, date)%>%
  arrange(datetime)%>%
  mutate(Tdiff = Temp - lag(Temp, 1)) %>%
  mutate(large = ifelse(Tdiff>5, "Y", "N")) 

Tdiff_distrib <- Tdiffs_all %>%
  group_by(station) %>%
  summarize(mean.tdiff = mean(Tdiff, na.rm = TRUE),
            max.tdiff = max(Tdiff, na.rm = TRUE),
            n.large = sum(large == "Y", na.rm = TRUE),
            n = n()) %>%
  mutate(percent.large = n.large/n * 100)

ggplot(Tdiffs_all) +
  geom_boxplot(aes(x = station, y =Tdiff))

ggplot(Tdiff_distrib, aes(x = station, y = percent.large)) + 
  geom_point()

```


## How much data are being removed?
```{r Data removal}

removed_all <- temp_q4 %>%
  summarize(Init = n(),
            QC1 = sum(Flag_QC1=="Y"),
            QC2 = sum(Flag_QC2_b == "Y"),
            QC3 = sum(Flag_QC3 == "Y", na.rm = TRUE),
            QC4 = sum(Flag_QC4 == "Y"),
            Remaining = sum(Flag_QC1=="N" & Flag_QC2_b == "N" & Flag_QC3 =="N" & Flag_QC4 =="N", na.rm = TRUE),
            Prop = round(Remaining/Init*100,1))


removed_sta <- temp_q4 %>%
  group_by(station) %>%
  summarize(Init = n(),
            QC1 = sum(Flag_QC1=="Y"),
            QC2 = sum(Flag_QC2_b == "Y"),
            QC3 = sum(Flag_QC3 == "Y", na.rm = TRUE),
            QC4 = sum(Flag_QC4 == "Y"),
            Remaining = sum(Flag_QC1=="N" & Flag_QC2_b == "N" & Flag_QC3 =="N" & Flag_QC4 =="N", na.rm = TRUE),
            Prop = round(Remaining/Init*100,1)) %>%
  arrange(Prop)

a <- as.list(removed_sta)
```


## Write files

```{r WriteFile, message = FALSE}
library(readr)

saveRDS(temp_q4, ".rds")
write_csv(temp_q4, "QC/temp_all_qc.csv")

### Individual files to csv

# write each file as a csv
allsta_q5$station <- as.factor(allsta_q5$station) # need to factorize the "stations"
#Get the list of unique MP names
for (name in levels(allsta_q5$station)) {
  #Subset the data station
  tmp=subset(allsta_q5,station==name)
  #Create a new filename for each station. Designate the folder you want the files in.
  fn=paste('station_files/stations_qa/postoutlier/',name, "_q5.csv", sep="")
  #Save the CSV file for each station
  write_csv(tmp,fn)
}

```


