---
title: "DownloadData_CDEC"
author: "Catarina Pien"
date: "7/6/2020"
output: html_document
---

Water Temperature Synthesis
Download code adapted from Travis Hinkelmann (Cramer Fish Sciences) and William Anderson (Water Board) (personal communication)
This code downloads water temperature data from CDEC (http://cdec.water.ca.gov/)
For this example, data are downloaded through 2019 and converted to hourly data

Clear the environment

```{r clear, include = FALSE}
rm(list=ls(all=TRUE))
```

Load Packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(data.table) #rbindlist()
library(lubridate) #today()
library(CDECRetrieve) #cdec_datasets
library(readr)

# To get CDEC Retrieve initially:  
# install roxygen2 (normal install method)
# install.packages("https://cran.r-project.org/src/contrib/Archive/CDECRetrieve/CDECRetrieve_0.1.4.tar.gz", repos=NULL, method = "libcurl")
# Or use winzip to unzip the files, copy folder into the .libPaths() specified (or go to Tools Install to check where lib is)
# Easiest way: devtools::install_github("flowwest/CDECRetrieve")
```


Download information about what data are collected by stations (different sensors)
Filter out which stations collect event/hourly temperature data

```{r Station sensors, message = FALSE}

# List of all stations
sta_all<-c("BAC", "BET", "BLP", "CSE", "CYG", "FAL", "FLT", "FRK",
          "GOD", "GYS", "GZB", "GZL", "HON", "HUN", "IBS", "MDM", "MHO", "MOK", "MRZ", "MSL",
          "NMR", "OBI", "ODM", "OH4", "OLD", "OSJ", "PCO", "PPT", "ROR", "RSL", "RYC",
          "SMR", "SNC", "SUR", "TEA", "VCU", "VOL", 
          "BDL", "BLL", "DLC", "DWS", "FPT", "GES", "GLN", "GSS", "HWB", "LIB", "LIS", "MAL", "MIR", 
          "NSL", "RCS", "RVB", "RYF", "RYI", "SDI", "SOI", "SRH", "SRV", "SSI", "SSS", "SUT", "SXS","TMS", "TSL",
          "ANH", "BDT", "BIR", "DGL", "DSJ", "FCT", "GCT", "GLC", "GLE", "HLT", "HOL", "LPS",
          "MAB", "MHR", "MRU", "MRX", "MSD", "MTB", "MUP", "OAD", "OBD", "OH1", "ORI", "ORM", 
          "ORQ", "ORX", "PDC", "PRI", "RRI", "SGA", "SJC", "SJD", "SJG", "SJJ", "SJL", "SJR", 
          "TPI", "TRN", "TWA", "TWI", "WCI", "RIP",
          "DAR", "ECD", "MKN", "SR3", "SUS", "SWE", "VNS", "SJR",
          "ANC", "BKS", "CCS", "CLL", "CNT", "CPP", "DMC", "EMM", "FRP", "HBP", "HLL",
          "OBI", "JER", "PCT", "PTS", "RIV", "ROR", "SAL", "STI", "UNI", "VIC", "VOL", "MRZ",
          "ANH", "BDL", "BLL", "DV7", "GLN", "MAL", "MSD", "MTB", "NSL", "VER", "RPN", "RVB", "SJL", "SRH",
          "BKS", "CLC", "CPP", "DV7", "DYR", "HBP")

# Filter out list of unique stations (some are in there multiple times)
sta <- sort(unique(sta_all))

### First download dataset info ---------------------------------------------

# Loop to get info on what sensors are available for each station
# Based on station list above
sensordataset <- list() 
for(i in 1:length(sta)){
  dataset <- cdec_datasets(sta[i])
  dataset$station <- sta[i]  # just for an identifier
  sensordataset[[i]] <- dataset
} 

# Bind into dataframe 
cdec_datasets_df <-rbindlist(sensordataset)   #** LIST INTO DATAFRAME **

# Remove unnecessary objects to save space
rm(dataset)
rm(sensordataset)

# Include only stations with event and hourly water temperature data
# Sensor 25 = Temp_C
# Sensor 146 = Temp_F
cdec_temp <- cdec_datasets_df %>% 
  filter(sensor_number == 25 | sensor_number == 146) %>% 
  filter(duration !="daily") %>%
  arrange(station) %>%
  mutate(days = end-start)

```

Download Raw Data from CDEC
These are at Pacific Daylight Time 
See https://info.water.ca.gov/misc/sql_dates.html for information about how CDEC deals with Daylight Savings Time
Split up into 4 sets of stations: 
* Event/Fahrenheit
* Event/Celsius
* Hourly/Fahrenheit
* Hourly/Celsius

```{r Download, message = FALSE}

###################################### Event Data - Fahrenheit ##############################

### Define list of stations ----------------------------------

# Delta/Mokelumne/East Bay, sacR, sanJR (these are designations from CDEC) - this is how stations 
# are ordered below, and is why they are not in alphabetical order

sta_Ev_F <- c("BAC", "BET", "BLP", "CSE", "CYG", "FAL", "FLT", "FRK",
          "GOD", "GYS", "GZB", "GZL", "HON", "HUN", "IBS", "MDM", "MHO", "MOK", "MRZ", "MSL",
          "NMR", "OBI", "ODM", "OH4", "OLD", "OSJ", "PCO", "PPT", "ROR", "RSL", "RYC",
          "SMR", "SNC", "SUR", "TEA", "VCU", "VOL",
          "BDL", "BLL", "DLC", "DWS", "FPT", "GES", "GLN", "GSS", "HWB", "LIB", "LIS", "MAL",
          "MIR", "NSL", "RCS", "RVB", "RYF", "RYI", "SDI", "SOI", "SRH", "SRV", "SSI", "SSS", "SUT", "SXS",
          "TMS", "TSL", "ANH", "BDT", "BIR", "DGL", "DSJ", "FCT", "GCT", "GLC", "GLE", "HLT", "HOL", "LPS",
          "MAB", "MHR", "MRU", "MRX", "MSD", "MTB", "MUP", "OAD", "OBD", "OH1", "ORI", "ORM", 
          "ORQ", "ORX", "PDC", "PRI", "RIP", "RRI", "SGA", "SJC", "SJD", "SJG", "SJJ", "SJL", "SJR",
          "TPI", "TRN", "TWA", "TWI", "WCI", "RIP")

### Define rest of the sensor information desired -------------
# Start and end dates - these will remain the same throughout
start <- "1986-01-01"
end <- "2019-12-31"

# Sensor number, time interval - these are different for each set of stations
sensor1 <- "25" # Water Temperature, Celsius
interval1 <- "E" # Event = every 15 minutes

### Download data, bind, write --------------------------------------------
Temp_Event_F_Raw <- lapply(sta_Ev_F, 
                 function(x){
                   cdec_query(station = x,
                              sensor_num = sensor1,
                              dur_code = interval1,
                              start_date = start,
                              end_date = end)
                 })

Temp_E_F_Raw_df <- bind_rows(Temp_Event_F_Raw) # bind rows into data frame
write_csv(Temp_E_F_Raw_df, "Tempdata/Raw/Temp_E_F_raw.csv") #write data
saveRDS(Temp_E_F_Raw_df, "Tempdata/Raw/Temp_E_F_raw.rds") #write rds

###################################### Event Data - Celsius ##############################

### Define stations, sensor, interval ------------------------------------------
sta_Ev_C <- c("DAR", "ECD", "MKN", "SJR", "SR3", "SUS", "SWE", "VNS")

# Sensor number, time interval
sensor2 <- "146" # Water Temperature, Fahrenheit
interval2 <- "E" # Event: every 15 minutes

### Download data, bind, write --------------------------------------------
Temp_Event_C_Raw <- lapply(sta_Ev_C, 
                 function(x){
                   cdec_query(station = x,
                              sensor_num = sensor2,
                              dur_code = interval2,
                              start_date = start,
                              end_date = end)
                 })

Temp_E_C_Raw_df <- bind_rows(Temp_Event_C_Raw) # bind into a data frame

write_csv(Temp_E_C_Raw_df, "Tempdata/Raw/Temp_E_C_raw.csv") #write data
saveRDS(Temp_E_C_Raw_df, "Tempdata/Raw/Temp_E_C_raw.rds") #write rds


###################################### Hourly Data - Fahrenheit ##############################

### Define stations, sensor, interval ------------------------------------------
sta_H_F <- c("ANC", "ANH", "BAC", "BDL", "BLL", "CCS", "CLL", "CNT", "CPP", "DLC", "DMC", "DV7",
             "EMM", "FRP", "GLC", "GLN", "GOD", "GYS", "HBP", "HLL", "HLT", "HUN", "IBS", 
             "JER", "MAL", "MDM", "MRZ", "MSD", "MSL", "MTB", "NSL", 
             "OBI", "OH1", "OH4", "OSJ", "PCT", "PPT", "PTS", "RIV", "ROR", "RPN", "RVB", 
             "SAL", "SJL", "SJR", "SNC", "SRH", "STI", "UNI", "VER", "VIC", "VOL")

# Specify sensor, time interval
sensor3 <- "25" # 25 = Water Temperature, celsius
interval3 <- "H" # H = Hourly data

### Download data, bind, write --------------------------------------------
Temp_Hourly_F_Raw <- lapply(sta_H_F, 
                 function(x){
                   cdec_query(station = x,
                              sensor_num = sensor3,
                              dur_code = interval3,
                              start_date = start,
                              end_date = end)
                 })

Temp_H_F_Raw_df <- bind_rows(Temp_Hourly_F_Raw) # bind into df
write_csv(Temp_H_F_Raw_df, "Tempdata/Raw/Temp_H_F_raw.csv") #write data
saveRDS(Temp_H_F_Raw_df, "Tempdata/Raw/Temp_H_F_raw.rds") #write rds


###################################### Hourly Data - Celsius ##############################

### Define stations, sensor, interval ------------------------------------------
sta_H_C <- c("BKS", "CLC", "CPP", "DV7", "DYR", "HBP", "SJR")
sensor4 <- "146" # Water Temperature, Fahrenheit
interval4 <- "H" # Hourly interval


### Download data, bind, write --------------------------------------------
Temp_Hourly_C_Raw <- lapply(sta_H_C, 
                 function(x){
                   cdec_query(station = x,
                              sensor_num = sensor4,
                              dur_code = interval4,
                              start_date = start,
                              end_date = end)
                 })

Temp_H_C_Raw_df <- bind_rows(Temp_Hourly_C_Raw) # bind into df
write_csv(Temp_H_C_Raw_df, "Tempdata/Raw/Temp_H_C_raw.csv") #write data
saveRDS(Temp_H_C_Raw_df, "Tempdata/Raw/Temp_H_C_raw.rds") #write rds

# Remove some files
rm(Temp_Event_F_Raw, Temp_Event_C_Raw, Temp_Hourly_C_Raw, Temp_Hourly_F_Raw)
```


Standardize data to Celsius
Merge data into one dataset
Write file of merged data

```{r Standardize data, message = FALSE}

# Merge Fahrenheit event and hourly data together
# Add column Temp (converts F to C) 
# Remove and rename columns
Temp_F <- rbind(Temp_E_F_Raw_df, Temp_H_F_Raw_df)
Temp_FtoC <- Temp_F %>% mutate(Temp = round((parameter_value-32)/1.8,1))
Temp_C_1 <- Temp_FtoC %>% 
  select(-c(agency_cd, parameter_cd, parameter_value)) %>%
  rename(station = location_id)

# Merge Celsius event and hourly data together | Rm and rename columns
Temp_C <- rbind(Temp_E_C_Raw_df, Temp_H_C_Raw_df)
Temp_C_2 <- Temp_C %>% 
  select(-c(agency_cd, parameter_cd)) %>% 
  rename(station = location_id,
         Temp = parameter_value)

# Remove some files
rm(Temp_F, Temp_FtoC, Temp_C)

# Merge converted temp data frames together 
Temp_all_std <- rbind(Temp_C_1, Temp_C_2)
Temp_all_std <- rename(Temp_all_std,
  Station =station,
  Datetime = datetime)
saveRDS(Temp_all_std, "Tempdata/Std/Temp_all_std.rds") # Write rds
write_csv(Temp_all_std, "Tempdata/Std/Temp_all_std.csv") # write csv

# This data was used as the raw table file for EDI.

```


Write individual files for each station
CSV - includes event and hourly data all combined

```{r Individual station files, message = FALSE}
Temp_all_std$station <- as.factor(Temp_all_std$station) # need to factorize the "stations"
#Get the list of unique station names
for (name in levels(Temp_all_std$station)) {
  #Subset the data station
  tmp=subset(Temp_all_std,station==name)
  #Create a new filename for each station. Designate the folder you want the files in.
  fn=paste('Tempdata/Std/Individual/',name, "_std_sin.csv", sep="")
  #Save the CSV file for each station
  write_csv(tmp,fn)
}
```

Convert data to hourly by picking the first value of each hour

```{r Hourly}

# In case you need to modify anything without re-downloading everything
# Temp_all_std <- readRDS("Tempdata/Std/Temp_all_std.rds")

# Add some columns to sort by date/time object types
Temp_all_std$Station <- as.factor(Temp_all_std$Station)
Temp_all_std$Date <- date(Temp_all_std$Datetime)
Temp_all_std$year <- year(Temp_all_std$Datetime)
Temp_all_std$month <- month(Temp_all_std$Datetime)
Temp_all_std$hour <- hour(Temp_all_std$Datetime)
Temp_all_std$minute <- minute(Temp_all_std$Datetime)

# Remove any row where Temp = NA or datetime = NA
temp_H_0 <- Temp_all_std %>%
  filter(!is.na(Temp)) %>%
  filter(!is.na(Datetime)) # need this for anomalize later or it won't run

# Convert temperature data to hourly
temp_H <- temp_H_0 %>%
  group_by(Station, Date, hour) %>% #group (calculations) by these vars
  arrange(Station, Date, hour, minute) %>% #arrange in order of these vars to visualize duplication
  slice(1) %>% #keep only the first value for each station, date, hour group so 1 value/hour
  ungroup()

# Check that they are all good!
check <- temp_H %>%
  group_by(Station, Date, hour)%>%
  summarize(vals = n())
which(check$vals >1) # this should be 0

# Remove extra variables 
temp_H_f <- temp_H %>%
  select(c(Station, Datetime, Temp, Date, hour)) %>%
    rename(Hour = hour)

# Write data
saveRDS(temp_H_f, "Tempdata/Hourly/Temp_all_H.rds") # Write rds
write_csv(temp_H_f, "Tempdata/Hourly/Temp_all_H.csv") # write csv

```

