---
title: "CDEC_QA_comparisons"
author: "Catarina Pien"
date: "September 25, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---
## Comparison of CDEC Data with Counterparts in Water Data Library and USGS National Water Information System

Compare same sites between CDEC - DWR Water Data Library and CDEC - USGS NWIS

Load Files into appropriate formats

```{r loading, eval = FALSE, include = FALSE, message = FALSE, warning = FALSE}
rm(list=ls(all=TRUE))

library(readr)

setwd("P:/ClimateChange/R_code")
# Read files, round all temperatures to one decimal place

FCT_WDL <- read_csv("Comparisons_QA_CDEC/FCT_WDL.csv")
FCT_std <- read_csv("Comparisons_QA_CDEC/FCT_std.csv")
FCT_WDL$Temp <- as.numeric(format(round(FCT_WDL$Temp, 1), nsmall=1))
FCT_std$Temp <- as.numeric(format(round(FCT_std$Temp, 1), nsmall=1))

TMS_WDL <- read_csv("Comparisons_QA_CDEC/TMS_WDL.csv")
TMS_std <- read_csv("Comparisons_QA_CDEC/TMS_std.csv")
TMS_WDL$Temp <- as.numeric(format(round(TMS_WDL$Temp, 1), nsmall=1))
TMS_std$Temp <- as.numeric(format(round(TMS_std$Temp, 1), nsmall=1))

OSJ_WDL <- read_csv("Comparisons_QA_CDEC/OSJ_WDL.csv")
OSJ_std <- read_csv("Comparisons_QA_CDEC/OSJ_std.csv")
OSJ_WDL$Temp <- as.numeric(format(round(OSJ_WDL$Temp, 1), nsmall=1))
OSJ_std$Temp <- as.numeric(format(round(OSJ_std$Temp, 1), nsmall=1))

SOI_WDL <- read_csv("Comparisons_QA_CDEC/SOI_WDL.csv")
SOI_std <- read_csv("Comparisons_QA_CDEC/SOI_std.csv")
SOI_WDL$Temp <- as.numeric(format(round(SOI_WDL$Temp, 1), nsmall=1))
SOI_std$Temp <- as.numeric(format(round(SOI_std$Temp, 1), nsmall=1))

GSS_NWIS <- read_csv("Comparisons_QA_CDEC/GSS_NWIS.csv")
GSS_std <- read_csv("Comparisons_QA_CDEC/GSS_std.csv")
GSS_NWIS$Temp <- as.numeric(format(round(GSS_NWIS$Temp, 1), nsmall=1))
GSS_std$Temp <- as.numeric(format(round(GSS_std$Temp, 1), nsmall=1))

LPS_NWIS <- read_csv("Comparisons_QA_CDEC/LPS_NWIS.csv")
LPS_std <- read_csv("Comparisons_QA_CDEC/LPS_std.csv")
LPS_NWIS$Temp <- as.numeric(format(round(LPS_NWIS$Temp, 1), nsmall=1))
LPS_std$Temp <- as.numeric(format(round(LPS_std$Temp, 1), nsmall=1))

PRI_NWIS <- read_csv("Comparisons_QA_CDEC/PRI_NWIS.csv")
PRI_std <- read_csv("Comparisons_QA_CDEC/PRI_std.csv")
PRI_NWIS$Temp <- as.numeric(format(round(PRI_NWIS$Temp, 1), nsmall=1))
PRI_std$Temp <- as.numeric(format(round(PRI_std$Temp, 1), nsmall=1))

SJJ_NWIS <- read_csv("Comparisons_QA_CDEC/SJJ_NWIS.csv")
SJJ_std <- read_csv("Comparisons_QA_CDEC/SJJ_std.csv")
SJJ_NWIS$Temp <- as.numeric(format(round(SJJ_NWIS$Temp, 1), nsmall=1))
SJJ_std$Temp <- as.numeric(format(round(SJJ_std$Temp, 1), nsmall=1))

# Standardize time formats
FCT_WDL$datetime <- as.POSIXct(FCT_WDL$datetime, format = "%m/%d/%Y %H:%M")
FCT_WDL$datetime <- as.POSIXct(FCT_WDL$datetime, format = "%Y-%M-%D %H:%M:%S")
TMS_WDL$datetime <- as.POSIXct(TMS_WDL$datetime, format = "%m/%d/%Y %H:%M")
TMS_WDL$datetime <- as.POSIXct(TMS_WDL$datetime, format = "%Y-%M-%D %H:%M:%S")
OSJ_WDL$datetime <- as.POSIXct(OSJ_WDL$datetime, format = "%m/%d/%Y %H:%M")
OSJ_WDL$datetime <- as.POSIXct(OSJ_WDL$datetime, format = "%Y-%M-%D %H:%M:%S")
SOI_WDL$datetime <- as.POSIXct(SOI_WDL$datetime, format = "%m/%d/%Y %H:%M")
SOI_WDL$datetime <- as.POSIXct(SOI_WDL$datetime, format = "%Y-%M-%D %H:%M:%S")
GSS_NWIS$datetime <- as.POSIXct(GSS_NWIS$datetime, format = "%m/%d/%y %H:%M")
GSS_NWIS$datetime <- as.POSIXct(GSS_NWIS$datetime, format = "%Y-%M-%D %H:%M:%S")
LPS_NWIS$datetime <- as.POSIXct(LPS_NWIS$datetime, format = "%m/%d/%y %H:%M")
LPS_NWIS$datetime <- as.POSIXct(LPS_NWIS$datetime, format = "%Y-%M-%D %H:%M:%S")
PRI_NWIS$datetime <- as.POSIXct(PRI_NWIS$datetime, format = "%m/%d/%y %H:%M")
PRI_NWIS$datetime <- as.POSIXct(PRI_NWIS$datetime, format = "%Y-%M-%D %H:%M:%S")
SJJ_NWIS$datetime <- as.POSIXct(SJJ_NWIS$datetime, format = "%m/%d/%y %H:%M")
SJJ_NWIS$datetime <- as.POSIXct(SJJ_NWIS$datetime, format = "%Y-%M-%D %H:%M:%S")

write_csv(FCT_WDL, "Comparisons_QA_CDEC/formatted/FCT_WDL_2.csv")
write_csv(FCT_std, "Comparisons_QA_CDEC/formatted/FCT_std_2.csv")
write_csv(TMS_WDL, "Comparisons_QA_CDEC/formatted/TMS_WDL_2.csv")
write_csv(TMS_std, "Comparisons_QA_CDEC/formatted/TMS_std_2.csv")
write_csv(OSJ_WDL, "Comparisons_QA_CDEC/formatted/OSJ_WDL_2.csv")
write_csv(OSJ_std, "Comparisons_QA_CDEC/formatted/OSJ_std_2.csv")
write_csv(SOI_WDL, "Comparisons_QA_CDEC/formatted/SOI_WDL_2.csv")
write_csv(SOI_std, "Comparisons_QA_CDEC/formatted/SOI_std_2.csv")
write_csv(GSS_NWIS, "Comparisons_QA_CDEC/formatted/GSS_NWIS_2.csv")
write_csv(GSS_std, "Comparisons_QA_CDEC/formatted/GSS_std_2.csv")
write_csv(LPS_NWIS, "Comparisons_QA_CDEC/formatted/LPS_NWIS_2.csv")
write_csv(LPS_std, "Comparisons_QA_CDEC/formatted/LPS_std_2.csv")
write_csv(PRI_NWIS, "Comparisons_QA_CDEC/formatted/PRI_NWIS_2.csv")
write_csv(PRI_std, "Comparisons_QA_CDEC/formatted/PRI_std_2.csv")
write_csv(SJJ_NWIS, "Comparisons_QA_CDEC/formatted/SJJ_NWIS_2.csv")
write_csv(SJJ_std, "Comparisons_QA_CDEC/formatted/SJJ_std_2.csv")
```


After files saved in correct formats, read files in.

```{r read, warning = FALSE, message = FALSE, results = FALSE}
library(readr)
setwd("P:/ClimateChange/R_code")

FCT_WDL <- read_csv("Comparisons_QA_CDEC/formatted/FCT_WDL_2.csv")
FCT_std <- read_csv("Comparisons_QA_CDEC/formatted/FCT_std_2.csv")
TMS_WDL <- read_csv("Comparisons_QA_CDEC/formatted/TMS_WDL_2.csv")
TMS_std <- read_csv("Comparisons_QA_CDEC/formatted/TMS_std_2.csv")
OSJ_WDL <- read_csv("Comparisons_QA_CDEC/formatted/OSJ_WDL_2.csv")
OSJ_std <- read_csv("Comparisons_QA_CDEC/formatted/OSJ_std_2.csv")
SOI_WDL <- read_csv("Comparisons_QA_CDEC/formatted/SOI_WDL_2.csv")
SOI_std <- read_csv("Comparisons_QA_CDEC/formatted/SOI_std_2.csv")
GSS_NWIS <- read_csv("Comparisons_QA_CDEC/formatted/GSS_NWIS_2.csv")
GSS_std <- read_csv("Comparisons_QA_CDEC/formatted/GSS_std_2.csv")
LPS_NWIS <- read_csv("Comparisons_QA_CDEC/formatted/LPS_NWIS_2.csv")
LPS_std <- read_csv("Comparisons_QA_CDEC/formatted/LPS_std_2.csv")
PRI_NWIS <- read_csv("Comparisons_QA_CDEC/formatted/PRI_NWIS_2.csv")
PRI_std <- read_csv("Comparisons_QA_CDEC/formatted/PRI_std_2.csv")
SJJ_NWIS <- read_csv("Comparisons_QA_CDEC/formatted/SJJ_NWIS_2.csv")
SJJ_std <- read_csv("Comparisons_QA_CDEC/formatted/SJJ_std_2.csv")

# Standardize time formats
FCT_WDL$datetime <- as.POSIXct(FCT_WDL$datetime, format = "%Y-%M-%D %H:%M:%S")
TMS_WDL$datetime <- as.POSIXct(TMS_WDL$datetime, format = "%Y-%M-%D %H:%M:%S")
OSJ_WDL$datetime <- as.POSIXct(OSJ_WDL$datetime, format = "%Y-%M-%D %H:%M:%S")
SOI_WDL$datetime <- as.POSIXct(SOI_WDL$datetime, format = "%Y-%M-%D %H:%M:%S")
GSS_NWIS$datetime <- as.POSIXct(GSS_NWIS$datetime, format = "%Y-%M-%D %H:%M:%S")
LPS_NWIS$datetime <- as.POSIXct(LPS_NWIS$datetime, format = "%Y-%M-%D %H:%M:%S")
PRI_NWIS$datetime <- as.POSIXct(PRI_NWIS$datetime, format = "%Y-%M-%D %H:%M:%S")
SJJ_NWIS$datetime <- as.POSIXct(SJJ_NWIS$datetime, format = "%Y-%M-%D %H:%M:%S")
```

### Plots (WDL)

Datasets have been downloaded and standardized.

Make some plots to compare datasets.

CDEC datasets were filtered so temperature is restricted from 0 - 30C.

* CDEC = blue
* Water Data Library = pink
* **Stations = OSJ, SOI, FCT, TMS**

```{r, echo = FALSE, message = FALSE, warning = FALSE}

library(ggplot2)
library(dplyr)

# OSJ
OSJ_std_QA <- OSJ_std%>%
  filter(Temp > 0 & Temp < 30)

ggplot() +
  geom_point(data = OSJ_std_QA, aes(x = datetime, y = Temp), col = "#123CCC", alpha = 0.3)+
  geom_point(data = OSJ_WDL, aes(x = datetime, y = Temp), col = "#ff6f69", alpha = 0.3)+
  labs(title = "OSJ") +
  theme_bw()

# SOI
SOI_std_QA <- SOI_std%>%
  filter(Temp > 0 & Temp < 30)

ggplot() +
  geom_point(data = SOI_std_QA, aes(x = datetime, y = Temp), col = "#123CCC", alpha = 0.3)+
  geom_point(data = SOI_WDL, aes(x = datetime, y = Temp), col = "#ff6f69", alpha = 0.3)+
  labs(title = "SOI") +
  theme_bw()

# FCT
FCT_std_QA <- FCT_std%>%
  filter(Temp > 0 & Temp < 30)

ggplot() +
  geom_point(data = FCT_std_QA, aes(x = datetime, y = Temp), col = "#123CCC", alpha = .3)+
  geom_point(data = FCT_WDL, aes(x = datetime, y = Temp), col = "#ff6f69", alpha = 0.3)+
  labs(title = "FCT") +
  theme_bw()


# TMS
TMS_std_QA <- TMS_std %>%
  filter(Temp > 0 & Temp < 30)

ggplot() +
  geom_point(data = TMS_std_QA, aes(x = datetime, y = Temp), col = "#123CCC", alpha = 0.3)+
  geom_point(data = TMS_WDL, aes(x = datetime, y = Temp), col = "#ff6f69", alpha = 0.3)+
  labs(title = "TMS") +
  theme_bw()


```

### Plots (NWIS)

* CDEC = blue
* NWIS = red

**Stations = PRI, SJJ, GSS, LPS**

```{r, echo = FALSE, message = FALSE, warning = FALSE}

library(ggplot2)
library(dplyr)

# PRI
PRI_std_QA <- PRI_std%>%
  filter(Temp > 0 & Temp < 30)

ggplot() +
  geom_point(data = PRI_std_QA, aes(x = datetime, y = Temp), col = "#123CCC", alpha = 0.3)+
  geom_point(data = PRI_NWIS, aes(x = datetime, y = Temp), col = "#CC1231", alpha = 0.3) +
  labs(title = "PRI") +
  theme_bw()

# SJJ
SJJ_std_QA <- SJJ_std%>%
  filter(Temp > 0 & Temp < 30)

ggplot() +
  geom_point(data = SJJ_std_QA, aes(x = datetime, y = Temp), col = "#123CCC", alpha = 0.3)+
  geom_point(data = SJJ_NWIS, aes(x = datetime, y = Temp), col = "#CC1231", alpha = 0.3)+
  labs(title = "SJJ") +
  theme_bw()

# GSS
GSS_std_QA <- GSS_std%>%
  filter(Temp > 0 & Temp < 30)

ggplot() +
  geom_point(data = GSS_std_QA, aes(x = datetime, y = Temp), col = "#123CCC", alpha = 0.3)+
  geom_point(data = GSS_NWIS, aes(x = datetime, y = Temp), col = "#CC1231", alpha = 0.3) +
  labs(title = "GSS") +
  theme_bw()

# LPS
LPS_std_QA <- LPS_std%>%
  filter(Temp > 0 & Temp < 30)

ggplot() +
  geom_point(data = LPS_std_QA, aes(x = datetime, y = Temp), col = "#123CCC", alpha = 0.3)+
  geom_point(data = LPS_NWIS, aes(x = datetime, y = Temp), col = "#CC1231", alpha = 0.3) +
  labs(title = "LPS") +
  theme_bw()



```


Try comparing temperature values by datetime - example of code but not results

In comments are the number of differences detected by comparing datasets by datetime. 

```{r compare, eval=FALSE}
library(testthat)
library(arsenal)

summary(compare(SOI_std_QA, SOI_WDL, by = "datetime")) # 107000 differences/ 110548 (0.97)
summary(compare(FCT_std_QA, FCT_WDL, by = "datetime")) # 108174 differences/ 121175 (0.89)
summary(compare(GSS_std_QA, GSS_NWIS, by = "datetime")) #69556 differences/ 203552 (0.34)
summary(compare(LPS_std_QA, LPS_NWIS, by = "datetime")) #192766 differences/ 203552 (0.95)
summary(compare(OSJ_std_QA, OSJ_WDL, by = "datetime")) #132525/ 304586 (0.44)
summary(compare(PRI_std_QA, PRI_NWIS, by = "datetime")) #156579/ 312562 (0.51)
summary(compare(TMS_std_QA, TMS_WDL, by = "datetime")) # 198558/ 367035 (0.54)
summary(compare(SJJ_std_QA, SJJ_NWIS, by = "datetime")) #86020/ 202837 (0.42)

```


### Experimental QA - The case of GSS

Add in some variables to sort and visualize the data (date, month)
```{r,  message = FALSE, warning = FALSE}
library(lubridate)
library(dplyr)
library(ggplot2)
library(scales)

# Give GSS different time sorting variables
GSS_std_QA$date <- as.Date(GSS_std_QA$datetime, format = "%Y-%M-%D")
GSS_std_QA$month <- month(GSS_std_QA$date)
GSS_std_QA$yrMon <- format(as.Date(GSS_std_QA$date), "%Y-%m")
GSS_std_QA$ymon1 <- as.Date(paste(GSS_std_QA$yrMon, "-01", sep=""))

GSS_NWIS$date <- as.Date(GSS_NWIS$datetime, format = "%Y-%M-%D")
GSS_NWIS$month <- month(GSS_NWIS$date)
GSS_NWIS$yrMon <- format(as.Date(GSS_NWIS$date), "%Y-%m")
GSS_NWIS$ymon1 <- as.Date(paste(GSS_NWIS$yrMon, "-01", sep=""))

```


#### Outliers

* Calculate outliers based on the "normal" equation (quartile 1-3)
* Convert outliers to "NA"

```{r, warning = FALSE, message = FALSE}

# Calculate outliers 
GSS_out <- GSS_std_QA %>%
  group_by(ymon1) %>%
  summarize(Q1 = quantile(Temp, probs = 0.25), 
            Q3 = quantile(Temp, probs = 0.75),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR)

# Merge together ul and ll into the original file with temperatures
GSS_QA2 <- merge(GSS_std_QA, GSS_out, by = "ymon1")

# Convert values under ll and above ul into "NA"
GSS_QA2$Temp2 <- ifelse(GSS_QA2$Temp < GSS_QA2$ll | GSS_QA2$Temp> GSS_QA2$ul, "NA", GSS_QA2$Temp)
GSS_QA2$Temp2 <- as.numeric(GSS_QA2$Temp2)


```


Same as above, but with less stringent bounds for the outliers (0.1 and 0.9)

```{r , warning = FALSE, message = FALSE}
## Less stringent
GSS_out2 <- GSS_std_QA %>%
  group_by(ymon1) %>%
  summarize(Q1 = quantile(Temp, probs = 0.1), 
            Q3 = quantile(Temp, probs = 0.9),
            IQR = Q3-Q1,
            ul = Q3 + 1.5 * IQR,
            ll = Q1 - 1.5 * IQR)

# Merge together ul and ll into the original file with temperatures
GSS_QA3 <- merge(GSS_std_QA, GSS_out2, by = "ymon1")

# Convert values under ll and above ul into "NA"
GSS_QA3$Temp2 <- ifelse(GSS_QA3$Temp < GSS_QA2$ll | GSS_QA3$Temp> GSS_QA3$ul, "NA", GSS_QA3$Temp)
GSS_QA3$Temp2 <- as.numeric(GSS_QA3$Temp2)
```


#### Plots!

##### Date vs Temp

Plots go from least QA to most QA: 

* Original
* Original QA (limits above 0 and below 30)
* 0.25-0.75
* 0.1 - 0.9
* NWIS QA

```{r echo = FALSE, message = FALSE, warning = FALSE, error = TRUE, fig.height = 5, fig.width=9}

# Original
ggplot() +
  geom_point(data = GSS_std, aes(x = datetime, y = Temp))+
  scale_x_datetime(breaks = date_breaks("4 months"), labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "Original data with no QA") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 13),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# Original QA
ggplot() +
  geom_point(data = GSS_std, aes(x = date, y = Temp, col = factor(month)))+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "Simple QA with lower and upper limits") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 13),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# Medium stringent
ggplot()+
  geom_point(data = GSS_QA3, aes(x = date, y = Temp2, col = factor(month)))+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "QA with some outliers removed") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# Most stringent
ggplot()+
  geom_point(data = GSS_QA2, aes(x = date, y = Temp2, col = factor(month)))+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "QA with more outliers removed - more stringent") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# NWIS
ggplot()+
  geom_point(data = GSS_NWIS, aes(x = date, y = Temp, col = factor(month)))+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "NWIS QA") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))
```

Plots go from least QA to most QA: 
* Original QA (limits above 0 and below 30)
* 0.25-0.75
* 0.1 - 0.9
* NWIS QA

##### Boxplots
```{r, echo = FALSE, message = FALSE, warning = FALSE, error = TRUE, fig.height = 5, fig.width=9}
GSS_std_QA1 <- GSS_std_QA[50000:170000,]
# Original QA
ggplot() +
  geom_boxplot(data = GSS_std_QA1, aes(x = ymon1, y = Temp, group = factor(ymon1), 
                                      col = factor(month)))+
    scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
    labs(y = "Temperature (degC)",
       title = "Simple QA with lower and upper limits") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# medium stringent
ggplot() +
  geom_boxplot(data = GSS_QA3, aes(x = ymon1, y = Temp2, group = factor(ymon1),
                                   col = factor(month)))+
    scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
    labs(y = "Temperature (degC)",
       title = "QA with less outliers removed - less stringent") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# most stringent
ggplot() +
  geom_boxplot(data = GSS_QA2, aes(x = ymon1, y = Temp2, group = factor(ymon1),
                                   col = factor(month)))+
   scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "QA with more outliers removed - more stringent") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# NWIS
ggplot() +
  geom_boxplot(data = GSS_NWIS, aes(x = ymon1, y = Temp, group = factor(ymon1),
                                   col = factor(month)))+
   scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
    labs(y = "Temperature (degC)",
       title = "NWIS QA") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

```


##### By month (point plot)

Plots go from least QA to most QA: 

* Original
* Original QA (limits above 0 and below 30)
* 0.25-0.75
* 0.1 - 0.9
* NWIS QA


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width=9}

# Original data
ggplot() +
  geom_point(data = GSS_std_QA, aes(x = ymon1, y = Temp, col = factor(month)))+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "Simple QA with lower and upper limits") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# moderate stringent
ggplot()+
  geom_point(data = GSS_QA3, aes(x = ymon1, y = Temp2, group = factor(ymon1),
                                 col = factor(month)))+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "QA with less outliers removed - less stringent") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# most stringent
ggplot()+
  geom_point(data = GSS_QA2, aes(x = ymon1, y = Temp2, col = factor(month)))+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "QA with more outliers removed - more stringent") +
  theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))

# NWIS
ggplot()+
  geom_point(data = GSS_NWIS, aes(x = ymon1, y = Temp, col = factor(month)))+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "NWIS QA") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        plot.title=element_text(hjust = 0.5))
```



##### Overlay with NWIS

* Less stringent
* More stringent

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width=9}

# less stringent
GSS_QA3$source <- "CDEC_ed"
GSS_QA3b <- GSS_QA3[,c(2,3,4,5,6,7,1,14,13)]
GSS_NWIS$source <- "NWIS"
GSS_NWIS$Temp2 <- GSS_NWIS$Temp
GSS_all <- rbind(GSS_QA3b, GSS_NWIS)

ggplot(GSS_all, aes(x = date, y = Temp2, col = source), alpha = 0.3) +
  geom_point()+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "Less stringent") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank())


# most stringent
GSS_QA2$source <- "CDEC_ed"
GSS_QA2b <- GSS_QA2[,c(2,3,4,5,6,7,1,14,13)]
GSS_NWIS$source <- "NWIS"
GSS_NWIS$Temp2 <- GSS_NWIS$Temp
GSS_all2 <- rbind(GSS_QA2b, GSS_NWIS)

ggplot(GSS_all2, aes(x = date, y = Temp2, col = source), alpha = 0.3) +
  geom_point()+
  scale_x_date(breaks = "4 months", labels = date_format("%b %Y"))+
  labs(y = "Temperature (degC)",
       title = "More stringent")+
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 14),
        axis.title.y = element_text(size = 13),
        axis.title.x = element_blank())


```



Summarize stats

```{r error = TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

GSS_std_QA$source <- "CDEC_o"
GSS_std_QA$Temp2 <- GSS_std_QA$Temp
GSS_all_o <- rbind(GSS_std_QA, GSS_all)

GSS_all_o_st <- GSS_all_o %>%
  group_by(yrMon, source) %>%
  summarize(
    mean = mean(Temp),
    min = min(Temp),
    max = max(Temp),
    number = n())

kable(GSS_all_o_st[1:nrow(GSS_all_o_st),], caption = "less stringent") %>%
  kable_styling(bootstrap_options = c("hover", full_width = F))

GSS_all_o2 <- rbind(GSS_std_QA, GSS_all2)

GSS_all2st <- GSS_all_o2 %>%
  group_by(yrMon, source) %>%
  summarize(
    mean = mean(Temp),
    min = min(Temp),
    max = max(Temp),
    number = n())

kable(GSS_all2st[1:nrow(GSS_all2st),], caption = "more stringent") %>%
  kable_styling(bootstrap_options = c("hover", full_width = F))


```

