---
title: "WaterTemp_QC_Analysis"
author: "Catarina Pien"
date: "4/24/2020"
output: 
  html_document:
    code_folding: hide
editor_options: 
  
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls(all=TRUE))
```

### Load Data

```{r load, include = FALSE, warning = FALSE}
library(data.table)
library(tidyverse)
library(dplyr)
library(readr)
library(plotly)
library(lubridate)

#create a list of the files from your target directory
path1 <- "TempData/Analysis/1year/"
path2 <- "TempData/Analysis/6month/"
path3 <- "TempData/Analysis/3month/"
files1 = list.files(path = path1, pattern="*.csv", full.names = TRUE)
oneyear = plyr::ldply(files1, read_csv)

files2 = list.files(path = path2, pattern="*.csv", full.names = TRUE)
sixmonth = plyr::ldply(files2, read_csv)

files3 = list.files(path = path3, pattern="*.csv", full.names = TRUE)
threemonth = plyr::ldply(files3, read_csv)

head(oneyear)
```

### Filter Data
* June - September only
* Only "clean" data to compare the three datasets
```{r filter, results=FALSE, warning = FALSE}
Temp12 <- oneyear %>% filter(AllFlags == "N,N,N,N,N,N") %>% filter(month>5 & month<10)
Temp6 = sixmonth %>% filter(AllFlags == "N,N,N,N,N,N") %>% filter(month>5 & month<10)
Temp3 = threemonth %>% filter(AllFlags == "N,N,N,N,N,N") %>% filter(month>5 & month<10)

Temp12$year <- ordered(Temp12$year)
Temp12$month <- ordered(Temp12$month)
Temp12$hour <- ordered(Temp12$hour)

Temp6$year <- ordered(Temp6$year)
Temp6$month <- ordered(Temp6$month)
Temp6$hour <- ordered(Temp6$hour)

Temp3$year <- ordered(Temp3$year)
Temp3$month <- ordered(Temp3$month)
Temp3$hour <- ordered(Temp3$hour)

```

# Analysis {.tabset}
## Maximum Temperatures {.tabset}

#### Compare results from 3 months, 6 months, 1 year for trend:
* Stations = longest/high variability (MAL), high temperatures (FRK, MSD, SJR, VCU),
low variability (RVB), QC4 (PPT), QC5 (CCS), QC6 (PTS)
* Max temps in June, July, August, September 
* Number of days >= 27C in June, July, August, September

### 1.  Max daily temperatures
Definitely see higher temperatures in the months12 trend at CCS and MAL.

```{r daily max, fig.width = 12, fig.height = 16, warning = FALSE, message = FALSE}

### Max daily temperatures --------------------------------------------------------------------------
max12 <- Temp12  %>% group_by(station, year, month, date) %>% summarize(max.temp12 = max(Temp)) %>% ungroup()
max6 <- Temp6  %>% group_by(station, year, month, date) %>% summarize(max.temp6 = max(Temp)) %>% ungroup()
max3 <- Temp3  %>% group_by(station, year, month, date) %>% summarize(max.temp3 = max(Temp)) %>% ungroup()

# Joins
max1 <- left_join(max12, max6)
max2 <- left_join(max1, max3)

# Long format
MaxAll <- pivot_longer(max2, cols = starts_with("max"), names_to = "trend", values_to = "MaxTemp")
MaxAll$trend <- ordered(MaxAll$trend, levels = c("max.temp3", "max.temp6", "max.temp12"))
levels(MaxAll$trend) <- gsub("max.temp", "months", levels(MaxAll$trend))

# Plot
ggplot(MaxAll, aes(x = date, y = MaxTemp, color = trend)) + geom_point(alpha = 0.6, size = 4) + facet_grid(rows = vars(station), scales = "free") +
    scale_x_date(date_breaks = "1 year") +
  theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14))

```

### 2. Max monthly temperatures
Definitely see higher temperatures in the months12 trend.
```{r monthly max, fig.width = 12, fig.height = 17, warning = FALSE, message = FALSE}
### Max monthly temperatures -------------------------------------------------------
max12mon <- max12 %>% group_by(station, year, month) %>% summarize(maxmon12 = max(max.temp12))
max6mon <- max6 %>% group_by(station, year, month) %>% summarize(maxmon6 = max(max.temp6))
max3mon <- max3 %>% group_by(station, year, month) %>% summarize(maxmon3 = max(max.temp3))

mon1 <- left_join(max12mon, max6mon)
mon2 <- left_join(mon1, max3mon)

# Long format
maxMonthLong <- pivot_longer(mon2, cols = starts_with("maxmon"), names_to = "trend", values_to = "MaxTemp")
maxMonthLong$trend <- ordered(maxMonthLong$trend, levels = c("maxmon3", "maxmon6", "maxmon12"))
levels(maxMonthLong$trend) <- gsub("maxmon", "months", levels(maxMonthLong$trend))

# Scatterplot
ggplot(maxMonthLong, aes(x = year, y = MaxTemp, color = trend)) + geom_point(alpha = 0.6, size = 4) + facet_grid(rows = vars(station), scales = "free") +
  theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14))

# Boxplot
ggplot(maxMonthLong, aes(x = year, y = MaxTemp, fill = trend)) + geom_boxplot(position = "dodge2") + facet_grid(rows = vars(station), scales = "free") +
  theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14))
```

### 3. Days per year with max temps >= 27
* Not a huge difference for the most part. 
* Greatest difference between the months12 (1 year) trend and the others. 
* VCU and PPT 2006 are likely true as there was a heat wave July 23-24. For some reason the 6-month trend cuts this off but the 3-month and 1-year do not. See plot of June-July temps for 2006. 
* MAL 2006 likely outliers

```{r max threshold, fig.width = 12, fig.height = 10, warning = FALSE, message = FALSE}
### Number of days max temp is >= 27C -------------------------------------------------------
max12days <- max12 %>% group_by(station, year) %>% summarize(nmax12 = sum(max.temp12 >= 27))
max6days <- max6 %>% group_by(station, year) %>% summarize(nmax6 = sum(max.temp6>=27))
max3days <- max3 %>% group_by(station, year) %>% summarize(nmax3 = sum(max.temp3>=27))

a <- left_join(max12days, max6days)
maxTempDays <- left_join(a, max3days)

# Long format
maxTempsLong <- pivot_longer(maxTempDays, cols = starts_with("nmax"), names_to = "trend", values_to = "ndays")
maxTempsLong$trend <- ordered(maxTempsLong$trend, levels = c("nmax3", "nmax6", "nmax12"))
levels(maxTempsLong$trend) <- gsub("nmax", "months", levels(maxTempsLong$trend))

# Plot maximum temperatures for the three trends 
maxPlots <- maxTempsLong %>% filter(ndays>0)

ggplot(maxPlots, aes(year, ndays, fill = trend)) + geom_col(position = "dodge2") + 
  facet_grid(rows = vars(station), scales = "free") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14))

# Check it out: 2006 MAL,VCU, PPT
hi1 <- Temp12 %>%
  filter(year ==  "2006" & (month == "6"|month == "7") & station %in% c("PPT", "VCU", "MAL"))

ggplot(hi1, aes(x = datetime, y = Temp )) + geom_point() + facet_grid(station~.) +
    labs(title = "2006 June-July Temps") +
    theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14))

# Check it out: 2006 VCU and PPT
mergemax1 <-  left_join(max12, max6)
mergemax2 <- left_join(mergemax1, max3)
print("Filter Max temperatures (1year) >= 26")
mergemax2 %>%
  filter(station %in% c("PPT", "VCU", "MAL"),
         max.temp12>=26) %>%
  print(n=50)

```

## Heat Wave Analysis
### 1. Download Air Temperature Stations: MAL, MSD, SJR

```{r airtemp dl, eval = FALSE, message = FALSE, warning = FALSE, fig.width = 12}
library(data.table) #rbindlist()
library(CDECRetrieve)#cdec_datasets

# Download air temperature data
# Stations
staAir <- c("SJR", "MSD", "MAL")
# Start and end dates - these will remain the same throughout
start <- "1986-01-01"
end <- "2019-12-31"

# Sensor number, time interval - these are different for each set of stations
sensor1 <- "4"
interval1 <- "H"

### Download data, bind, write --------------------------------------------
TempAir_Raw <- lapply(staAir, 
                 function(x){
                   cdec_query(station = x,
                              sensor_num = sensor1,
                              dur_code = interval1,
                              start_date = start,
                              end_date = end)
                 })

TempAir_Raw_df <- bind_rows(TempAir_Raw) # bind rows into data frame
str(TempAir_Raw_df)

TempAir_Raw_df$date <- date(TempAir_Raw_df$datetime)
TempAir_Raw_df$month <- (month(TempAir_Raw_df$datetime))
TempAir_Raw_df$year <- (year(TempAir_Raw_df$datetime))

# Change to Celsius
TempAir <- TempAir_Raw_df %>%
  rename(station = location_id) %>%
  mutate(AirTemp = round((parameter_value-32)/1.8,1)) %>%
  select(-c("parameter_cd", "parameter_value", "agency_cd"))

write.csv(TempAir, "TempData/AirTemp/AirTempC.csv")
```

### 2. Filter data, calculate max airtemp, join data frame 
* Filter to June-September
* Calculate max daily temperature for each station
* Calculate mean max daily temperature since 2010 for each station
* Join by date: max air temperatures with all water temp (includes flagged data)
```{r manipulate, warning = FALSE, message = FALSE }
# Read file written above
TempAir0 <- read_csv("TempData/AirTemp/AirTempC.csv")

# Filter to summer 
TempAir <- filter(TempAir0, month > 5 & month <10)

# Character dates 
# Using full temperature (unflagged, unfiltered dataset)
oneyear$day <-day(oneyear$date)
sixmonth$day <- day(sixmonth$date)
threemonth$day <- day(threemonth$date)
oneyear <- mutate(oneyear, 
                  datech = paste0(year, month, day))
sixmonth <- mutate(sixmonth, 
                   datech = paste0(year, month, day))
threemonth <- mutate(threemonth,
                     datech = paste0(year, month, day))


# Calculate average maximum temperature for all July-Septembers of past 10 years
MaxTempAir <- TempAir %>% 
  filter(year > 2009) %>%
  group_by(station, date) %>%
  summarize(max.airtemp = max(AirTemp)) %>%
  ungroup()

# Mean max summer temperatures: 
MeanMaxTempAir <- MaxTempAir %>%
  filter(!is.na(max.airtemp)) %>%
  group_by(station) %>%
  mutate(mean.max = round(mean(max.airtemp, na.rm = TRUE),2))

ggplot(MeanMaxTempAir, aes(max.airtemp)) + geom_histogram() + facet_wrap(~station) +
    theme_bw()+ theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14))

# For each station:
MaxTempAir %>%
  filter(!is.na(max.airtemp)) %>%
  group_by(station) %>%
  summarize(mean.max = round(mean(max.airtemp, na.rm = TRUE),2))

# Join water temp and air temp dataframes
Out12 <- inner_join(MeanMaxTempAir, oneyear, by = c("station", "date")) %>% 
  filter(Flag_QC1 == "N")
Out6 <- inner_join(MeanMaxTempAir, sixmonth, by = c("station", "date")) %>% 
  filter(Flag_QC1 == "N") 
Out3 <- inner_join(MeanMaxTempAir, threemonth, by = c("station", "date"))%>% 
  filter(Flag_QC1 == "N")

```

### 3. Flag heat waves, plot {.tabset}
* Look at overall relationship between water and air temp
* Look to see if air temp/ heat wave analysis is informative about whether an outlier is an outlier
* “The World Meteorological Organization defines it as five or more consecutive days during which the daily maximum temperature surpasses the average maximum temperature by 5 °C (9 °F) or more.”
* Flag QC4 (anomalize outliers) as boxes instead of dots 
* Color code heat waves by water and air temp (calculated by air temp)

#### Air-Water Pattern
* Just 2013 
* Pretty big variability
* Orange = air, blue = water 

```{r airwater, message = FALSE, warning = FALSE, fig.height = 9, fig.width = 12}
# Filter for just one summer

airwater <- left_join(TempAir, oneyear) %>% 
  filter(year == "2013", 
         AirTemp > 5 & AirTemp < 45,
         Temp > 0 & Temp <40)

ggplot(airwater) +
  geom_point(aes(x = datetime, y = AirTemp), color = "orange") +
  geom_point(aes(x = datetime, y = Temp), color = "blue") + 
  facet_grid(station~.) + 
  scale_x_datetime(date_breaks = "5 days") +
  scale_y_continuous(breaks = seq(10,40,by = 5)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14),
        legend.position = "bottom")

```


#### 12 month
* No anomalize outliers in this dataset
```{r heatwave, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 9}
### Flagging heat waves 
# Removed airtemp outliers that are > 45C
# Flag if airtemp > mean max air temp + 5
# Count number of occurrences in a row 
# Flag if occurrences >= 5
heat12 <- Out12 %>% 
  filter(max.airtemp < 45) %>%
  group_by(station) %>%
  mutate(HeatWave = ifelse(max.airtemp>mean.max +5, 1L, 0L)) %>%
  mutate(issame = cumsum(HeatWave == 0L)) %>%
  group_by(station, issame) %>%
  mutate(flag = ifelse(HeatWave == 1L, sum(HeatWave), 0L)) %>%
  ungroup() %>%
  mutate(FlagWave = ifelse(flag >=5, "Y", "N")) %>%
  select(-c(HeatWave, issame, flag, mean.max)) %>%
  rename(AirTemp = max.airtemp,
         WaterTemp = Temp)

# Long Format so we have temp broken out by air and water
LongHeat12 <- pivot_longer(heat12, cols = ends_with("Temp"), names_to = "Medium", values_to = "Temperature") %>%
  mutate(Type_HeatWave = as.factor(paste0(Medium, "_", FlagWave))) 

LongHeat12 %>%
  filter(Flag_QC4 == "Y")

# Plot temp vs date
ggplot(LongHeat12) + 
  geom_point(aes(x = date, y = Temperature, color = Type_HeatWave, shape = Flag_QC4), size = 3) +
  facet_grid(station~., scales = "free") +
  labs(x = "Date",
       y = "Temperature (C)", 
       title = "Temp by Date") +
 scale_color_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
  scale_x_date(date_breaks = "1 year") +
  scale_shape_manual(values = c(20, 15))+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14),
        legend.position = "bottom")

# Add date factor to be able to plot
LongHeat12$datech <- as.factor(LongHeat12$datech)

# Plot temp vs discrete date to get rid of spaces in between
ggplot(LongHeat12) + 
  geom_point(aes(x = datech, y = Temperature, color = Type_HeatWave, shape = Flag_QC4), size = 3) +
  facet_grid(station~., scales = "free") +
  labs(x = "Date",
       y = "Temperature (C)",
       title = "Temp by Discrete Date") +
 scale_color_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
    scale_x_discrete("DiscreteDate", breaks = c("201061", "201161",
                                               "201261","201361","201461","201561","201672",
                                               "201761","201861","201961")) +
  scale_shape_manual(values = c(20, 15))+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14),
        legend.position = "bottom")

```

#### 6 month
* Look at anomalize outliers to see if they occur during heat waves
* Not many outliers, mostly in 2011-June for MSD. LIkely outlier as no heat wave or air temp change detected

```{r 6month heatwave, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 9}
### Comparing trend = 6 month #####################################################
# Calculate heat waves
heat6 <- Out6 %>% 
  filter(max.airtemp < 45) %>%
  group_by(station) %>%
  mutate(HeatWave = ifelse(max.airtemp>mean.max+5, 1L, 0L)) %>%
  mutate(issame = cumsum(HeatWave == 0L)) %>%
  group_by(station, issame) %>%
  mutate(flag = ifelse(HeatWave == 1L, sum(HeatWave), 0L)) %>%
  ungroup() %>%
  mutate(FlagWave = ifelse(flag >=5, "Y", "N"))

# Long Format
LongHeat6 <- pivot_longer(heat6, cols = ends_with("Temp"), names_to = "Medium", values_to = "Temperature") %>%
  mutate(Type_HeatWave = as.factor(paste0(Medium, "_", FlagWave))) 

# Outliers
LongHeat6 %>%
  filter(Flag_QC4 == "Y") %>%
  filter(Medium == "max.airtemp") %>%
  print(n=50)

# Plot temp vs date
ggplot(LongHeat6) + 
  geom_point(aes(x = date, y = Temperature, color = Type_HeatWave, fill = Type_HeatWave,
                 shape = Flag_QC4), size = 3) +
  facet_grid(station~., scales = "free") +
  labs(x = "Date",
       y = "Temperature (C)",
       title = "Temp by Date") +
  scale_x_date(date_breaks = "1 year") +
 scale_color_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
  scale_fill_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
    scale_shape_manual(values = c(20, 15))+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14),
        legend.position = "bottom")

# Add date factor to be able to plot
LongHeat6$datech <- as.factor(LongHeat6$datech)

# Plot discrete date
ggplot(LongHeat6) + 
  geom_point(aes(x = datech, y = Temperature, color = Type_HeatWave, fill = Type_HeatWave, shape = Flag_QC4), size = 3) +
  facet_grid(station~., scales = "free") +
  labs(x = "Date",
       y = "Temperature (C)", 
       title = "Temp by Discrete Date") +
  scale_x_discrete("DiscreteDate", breaks = c("201061", "201161",
                                               "201261","201361","201461","201561","201672",
                                               "201761","201861","201961")) +
 scale_color_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
  scale_fill_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
  scale_shape_manual(values = c(20, 15))+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14), 
        legend.position = "bottom")

```

#### 3 month
* Look at anomalize outliers to see if they occur during heat waves
* Informative for some outliers for MSD and SJR
* Likely not outliers, unless air and temperature sensors connected
```{r 3month heatwave, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 9}
## Comparing trend = 3 month ###########################################################
# Calculate heat wave
heat3 <- Out3 %>% 
  filter(max.airtemp < 45) %>%
  group_by(station) %>%
  mutate(HeatWave = ifelse(max.airtemp>mean.max+5, 1L, 0L)) %>%
  mutate(issame = cumsum(HeatWave == 0L)) %>%
  group_by(station, issame) %>%
  mutate(flag = ifelse(HeatWave == 1L, sum(HeatWave), 0L)) %>%
  ungroup() %>%
  mutate(FlagWave = ifelse(flag >=5, "Y", "N"))

# Long format
LongHeat3 <- pivot_longer(heat3, cols = ends_with("Temp"), names_to = "Medium", values_to = "Temperature") %>%
  mutate(Type_HeatWave = as.factor(paste0(Medium, "_", FlagWave)))

# Outliers
LongHeat3 %>%
  filter(Flag_QC4 == "Y") %>%
  filter(Medium == "max.airtemp") %>%
  print(n = 100)

# Plot 
ggplot(LongHeat3) + 
  geom_point(aes(x = date, y = Temperature, color = Type_HeatWave, fill = Type_HeatWave, shape = Flag_QC4), size = 3) +
  facet_grid(station~., scales = "free") +
  labs(x = "Date",
       y = "Temperature (C)",
       title = "Temp by Date") +
  scale_x_date(date_breaks = "1 year") +
 scale_color_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
  scale_fill_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
  scale_shape_manual(values = c(20, 15))+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14),
        legend.position = "bottom")

# Factorize
LongHeat3$datech <- as.factor(LongHeat3$datech)

# Discrete date
ggplot(LongHeat3) + 
  geom_point(aes(x = datech, y = Temperature, color = Type_HeatWave, fill = Type_HeatWave, shape = Flag_QC4), size = 3) +
  facet_grid(station~., scales = "free") +
  labs(x = "Date",
       y = "Temperature (C)",
       title = "Temp by Discrete Date") +
  scale_x_discrete("DiscreteDate", breaks = c("201061", "201161",
                                               "201261","201361","201461","201561","201672",
                                               "201761","201861","201961")) +
 scale_color_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
  scale_fill_manual(values = c("lightsalmon", "sienna","lightblue", "blue")) +
  scale_shape_manual(values = c(20, 15))+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        strip.text = element_text(size = 15), 
        axis.text = element_text(size = 14), 
        axis.title = element_text(size = 14), 
        legend.text = element_text(size = 13), 
        legend.title= element_text(size = 14),
        legend.position = "bottom")

```

